---
title: "R Notebook"
output: html_notebook
---
```{r}
library(psych)
library(stringr)
library(ggplot2)
library(lmerTest)
library(report)
library(coin)
library(multcomp)
library(multgee)
library(plyr)
library(dplyr)
```

```{r}
# users taken out of analysis: user13 (had bugs on one technique), user30 (done it on laptop)
all_users <- list(12, 14, 15, 16, 17, 18, 19, 20, 21, 22, 23, 24, 25, 26, 27, 28, 31, 32)

survey_data <- results.survey %>% dplyr::select('V8', 'V26', 'V27', 'V28', 'V34', 'V35', 'V36', 'V37')
names(survey_data) <- c('subject', 'how_hard_to_learn_cgt', 'how_was_the_speed_cgt', 'technique_inspired_me_cgt', 'how_hard_to_learn_wws', 'ammount_suggestions_wws', 'suggestions_length_wws', 'technique_inspired_me_wws')

# remove first row since it holds the questions
survey_data <- survey_data %>% slice(2:n())
# only use subjects from user list
survey_data <- survey_data %>% filter(subject %in% all_users)


# rating scales from 1 to 5:
easy_hard_scale = list('very easy', 'easy', 'normal', 'hard', 'very hard')
agree_scale = list('Strongly disagree', 'Disagree', 'Neither agr. nor disagr.', 'Agree', 'Strongly agree')
speed_scale = list('way too slow', 'little too slow', 'just right', 'little too fast', 'way too fast')
amount_scale = list('way too low', 'little too low', 'just right', 'little too high', 'way too high')
length_scale = list('way too short', 'little too short', 'just right', 'little too long', 'way too long')

survey_data_text <- survey_data

# function to replace rating by index in scale list (see above)
replace_scale <- function(value, scale) match(value, scale)

# replace worded ratings by numeric ratings
survey_data <- survey_data %>% mutate(across(c("how_hard_to_learn_cgt", "how_hard_to_learn_wws"), replace_scale, easy_hard_scale))
survey_data <- survey_data %>% mutate(across(c("technique_inspired_me_cgt", "technique_inspired_me_wws"), replace_scale, agree_scale))
survey_data <- survey_data %>% mutate(across(c("how_was_the_speed_cgt"), replace_scale, speed_scale))
survey_data <- survey_data %>% mutate(across(c("ammount_suggestions_wws"), replace_scale, amount_scale))
survey_data <- survey_data %>% mutate(across(c("suggestions_length_wws"), replace_scale, length_scale))

#survey_data$how_hard_to_learn_cgt <- as.factor(survey_data$how_hard_to_learn_cgt)
#survey_data$how_hard_to_learn_wws <- as.factor(survey_data$how_hard_to_learn_wws)
#survey_data$technique_inspired_me_cgt <- as.factor(survey_data$technique_inspired_me_cgt)

survey_data$how_hard_to_learn_cgt <- as.factor(survey_data$how_hard_to_learn_cgt)
survey_data$how_hard_to_learn_wws <- as.factor(survey_data$how_hard_to_learn_wws)
survey_data$technique_inspired_me_cgt <- as.factor(survey_data$technique_inspired_me_cgt)
survey_data$technique_inspired_me_wws <- as.factor(survey_data$technique_inspired_me_wws)
survey_data$how_was_the_speed_cgt <- as.factor(survey_data$how_was_the_speed_cgt)
survey_data$ammount_suggestions_wws <- as.factor(survey_data$ammount_suggestions_wws)
survey_data$suggestions_length_wws <- as.factor(survey_data$suggestions_length_wws)

summary(survey_data)

print("usability")
summary(survey_data$how_hard_to_learn_cgt)
summary(survey_data$how_hard_to_learn_wws)

#describe(survey_data$how_hard_to_learn_cgt)
#describe(survey_data$how_hard_to_learn_wws)

print("inspiration")
summary(survey_data$technique_inspired_me_cgt)
summary(survey_data$technique_inspired_me_wws)

#describe(survey_data$technique_inspired_me_cgt)
#describe(survey_data$technique_inspired_me_wws)
#describe(survey_data$how_was_the_speed_cgt)
#describe(survey_data$ammount_suggestions_wws)
#describe(survey_data$suggestions_length_wws)
```


```{r}
boxplot(amount_backs ~ method, data = data_counts)
boxplot(amount_actions ~ method, data = data_counts)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
